Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-03-25 src/tex/ms.tex
discuss abiogenesis zone

The combination of a lack of \gls{UV} radiation today, which makes biosignature gases more detectable~\citep{Segura2005}, and a UV-rich past that may have enabled abiogenesis could make M~dwarfs the preferred targets for biosignature searches.
We note that relevant mission concepts, such as the Large Interferometer for Exoplanets~\citep[\life,][]{Quanz2022,Glauser2024}, include M-dwarf systems among their primary targets~\citep{Kammerer2018,Carrion-Gonzalez2023}.
Our findings underscore the importance of constraining the \gls{UV} emission profiles of \gls{EEC} host stars throughout their evolutionary stages to assess the viability of M-dwarf planets as testbeds for theories on the origins of life~\citep{Rimmer2021,Ranjan2023a}.

@@

\rev{We then calculated the ratio of the maximum past \gls{NUV} fluxes in K dwarfs and late M dwarfs in both photon number flux and energy flux regimes.
We found that this ``dynamic range'' is slightly larger in the photon number flux regime (\var{photon_flux_ratio}) compared to the energy flux regime (\var{integrated_flux_ratio}).
This suggests that our use of energy flux may slightly underestimate the variations in \gls{NUV} exposure across different stellar types, rendering our conclusions regarding the impact of host star spectral type on the UV Threshold Hypothesis conservative.
Our results are thus robust when transitioning between energy flux and photon number flux representations.}

>>>>

\revv{It was found that the ``abiogenesis zone'', defined as the region around a star where quiescent UV flux is sufficient to drive the prebiotic photochemistry necessary for building RNA precursors, does not necessarily overlap with the liquid water \gls{HZ} for stars cooler than K5 ($T_{\mathrm{eff}} \lesssim \SI{4400}{\kelvin}$), implying that such stars may be less favorable for initiating life via UV-driven chemistry~\citep{Rimmer2018}.
This conclusion, however, is based on a steady-state view of stellar UV fluxes and habitable zone boundaries.
In our work, we addressed this limitation by explicitly incorporating stellar evolution, including the high-UV early phase of M~dwarfs.
Our results suggest that planets orbiting M dwarfs may still be viable sites for abiogenesis under UV-dependent pathways.
In fact, the} combination of a lack of \gls{UV} radiation today, which makes biosignature gases more detectable~\citep{Segura2005}, and a UV-rich past that may have enabled abiogenesis could make M~dwarfs the preferred targets for biosignature searches.
We note that relevant mission concepts, such as the Large Interferometer for Exoplanets~\citep[\life,][]{Quanz2022,Glauser2024}, include M-dwarf systems among their primary targets~\citep{Kammerer2018,Carrion-Gonzalez2023}.
Our findings underscore the importance of constraining the \gls{UV} emission profiles of \gls{EEC} host stars throughout their evolutionary stages to assess the viability of M-dwarf planets as testbeds for theories on the origins of life~\citep{Rimmer2021,Ranjan2023a}.

@@

\revv{We also calculated } \rev{the ratio of the maximum past \gls{NUV} fluxes in K dwarfs and late M dwarfs in both photon number flux and energy flux regimes.
We found that this ``dynamic range'' is slightly larger in the photon number flux regime (\var{photon_flux_ratio}) compared to the energy flux regime (\var{integrated_flux_ratio}).
This suggests that our use of energy flux may slightly underestimate the variations in \gls{NUV} exposure across different stellar types, rendering our conclusions regarding the impact of host star spectral type on the UV Threshold Hypothesis conservative.
Our results are thus robust when transitioning between energy flux and photon number flux representations.}
